### 2024-04-25 Paper/paper.tex
fix latex documents

    \begin{figure}[ht!]
        \caption{Outcomes over time in all penalized hospitals}
        \includegraphics[scale=.5]{Objects/weighted_read_mort_graph.pdf}
        \label{fig:weighted_read_mort_graph}
    \end{figure}

@@

@@

    \import{Tables}{MD_noMD_readmort_synthdid.tex}

    \import{Tables}{forprofit_synth.tex}

    \import{Tables}{MD_noMD_uncompCMI_synth.tex}

    \import{Tables}{forprofit_uncompCMI_synth.tex}

@@

@@

\import{Tables}{forprofit_fullsample.tex}

@@

\import{Tables}{forprofit_matchsample.tex}

>>>>

    \begin{figure}[ht!]
    \centering
        \caption{Outcomes over time in all penalized hospitals}
        \includegraphics[width=\textwidth]{Objects/weighted_read_mort_graph.pdf}
        \label{fig:weighted_read_mort_graph}
    \end{figure}

@@

    \section{Endogenous Executive Team Changes?}

    \import{Tables}{change_analysis.tex}

@@

    \import{Tables}{MD_noMD_readmort_synth.tex}

    \import{Tables}{forprofit_readmort_synth.tex}

    %\import{Tables}{MD_noMD_uncompCMI_synth.tex}

    %\import{Tables}{forprofit_uncompCMI_synth.tex}

@@

\includegraphics[width=\textwidth]{Objects/has_doc_avg_map.pdf}

@@

\import{Tables}{forprofit_readmort_fullsample.tex}

@@

\import{Tables}{forprofit_readmort_matchsample.tex}
